### 2016-07-02 docs/INTERACTION_TABLES_MASTER.tex
R1 to ELE version

\begin{figure}[!ht]
  \centering
      \includegraphics[width=3in]{./components/formatted_figures/formatted_figureS4.png}
  \caption{Community-wide synchrony of species percent cover from model simulation experiments for the Idaho community with \textit{Artemisia tripartita} removed. Synchrony of species' percent cover for each study area are from simulation experiments with demographic stochasticity, environmental stochasticity, and interspecific competition present (``All Drivers''), demographic stochasticity removed (``No D.S.''), environmental stochasticity removed (``No E.S.''), interspecific competition removed (``No Comp.''), interspecific competition and demographic stochasticity removed (``No Comp. + No D.S.''), and interspecific competition and environmental stochasticity removed (``No Comp. + No E.S.''). Error bars represent the upper and lower 95\% quantiles from model simulations.}
\end{figure}

@@

\begin{table}[ht]
\centering
\caption{Comparisons between our analytical predictions and simulation results for synchrony of species' per capita growth rates. Analytical predictions represent two limiting cases where only demographic stochasticity is operating ($\phi_{R,\mathcal{M}_D}$) and where only environmental stochasticity is operating ($\phi_{R,\mathcal{M}_E}$). Simulated synchrony values come from our empirically-based, multi-species population models when simulated under conditions that match the limiting case conditions (e.g., environmental stochasticity and competition removed for $\mathcal{M}_D$).} 
{\normalsize
\begin{tabular}{lrrrr}
  \hline
Site & Predicted $\phi_{R,\mathcal{M}_D}$ & Simulated $\phi_{R,\mathcal{M}_D}$ & Predicted $\phi_{R,\mathcal{M}_E}$ & Simulated $\phi_{R,\mathcal{M}_E}$ \\ 
  \hline
New Mexico & 0.56 & 0.51 & 0.86 & 0.85 \\ 
  Arizona & 0.51 & 0.52 & 0.82 & 0.81 \\ 
  Kansas & 0.35 & 0.39 & 0.62 & 0.63 \\ 
  Montana & 0.31 & 0.33 & 0.47 & 0.49 \\ 
  Idaho & 0.29 & 0.31 & 0.43 & 0.41 \\ 
   \hline
\end{tabular}
}
\end{table}

\begin{table}[ht]
\centering
\caption{Percent differences of synchrony of per capita growth rates between each removal simulation experiment and the 'All Drivers' simulation.} 
\begin{tabular}{lrrrrr}
  \hline
simulation & 1New Mexico & 2Arizona & 3Kansas & 4Montana & 5Idaho \\ 
  \hline
1No D.S. & 5.00 & 4.94 & 7.13 & 4.42 & 10.10 \\ 
  2No Comp. + No D.S. & 4.25 & 2.08 & 7.61 & 4.39 & 8.10 \\ 
  4No Comp. & 0.98 & 0.06 & 4.84 & 1.01 & 0.11 \\ 
  5No E.S. & 40.14 & 33.20 & 47.84 & 38.52 & 9.28 \\ 
  6No Comp. + No E.S. & 45.95 & 41.48 & 38.21 & 33.07 & 20.33 \\ 
   \hline
\end{tabular}
\end{table}

\begin{table}[ht]
\centering
\caption{Correlations of species' year random effects for each site by term, where term refers to the random effect on the slope or the intercept.} 
\begin{tabular}{llrrr}
  \hline
site & term & growth & recruit & surv \\ 
  \hline
Arizona & intercept & 0.49 & -0.05 & 0.45 \\ 
  Arizona & slope & 0.68 &  & 0.15 \\ 
  Idaho & intercept & 0.46 & 0.38 & 0.29 \\ 
  Idaho & slope & 0.50 &  & 0.47 \\ 
  Kansas & intercept & 0.47 & 0.29 & 0.24 \\ 
  Kansas & slope & 0.18 &  & 0.16 \\ 
  Montana & intercept & 0.26 & 0.04 & 0.39 \\ 
  Montana & slope & 0.10 &  & 0.01 \\ 
  NewMexico & intercept & 0.54 & -0.15 & 0.64 \\ 
  NewMexico & slope & 0.32 &  & 0.15 \\ 
   \hline
\end{tabular}
\end{table}

\begin{table}[ht]
\centering
\caption{Average interaction coefficients across vital rates for each community.} 
\begin{tabular}{lrr}
  \hline
site & Interspecific Competition & Intraspecific Competition \\ 
  \hline
Arizona & -0.17 & -0.64 \\ 
  Idaho & -0.04 & -0.71 \\ 
  Kansas & 0.02 & -0.35 \\ 
  Montana & 0.04 & -0.98 \\ 
  NewMexico & -0.12 & -0.62 \\ 
   \hline
\end{tabular}
\end{table}

@@

\begin{table}[ht]
\centering
\caption{Interaction coefficients for survival regressions in Arizona.} 
\begin{tabular}{rrr}
  \hline
 & BOER & BORO \\ 
  \hline
BOER & -0.2791 & -0.0816 \\ 
  BORO & -0.0200 & -0.6101 \\ 
   \hline
\end{tabular}
\end{table}

\begin{table}[ht]
\centering
\caption{Interaction coefficients for recruitment regressions in Arizona.} 
\begin{tabular}{rrr}
  \hline
 & BOER & BORO \\ 
  \hline
BOER & -0.5304 & -0.3063 \\ 
  BORO & -0.5798 & -2.3237 \\ 
   \hline
\end{tabular}
\end{table}

@@

\begin{table}[ht]
\centering
\caption{Interaction coefficients for survival regressions in Idaho.} 
\begin{tabular}{rrrrr}
  \hline
 & ARTR & HECO & POSE & PSSP \\ 
  \hline
ARTR & -0.0236 & -0.0202 & 0.0314 & 0.0158 \\ 
  HECO & -0.0005 & -1.0206 & -0.0052 & 0.0125 \\ 
  POSE & 0.0001 & 0.0006 & -0.9091 & 0.0121 \\ 
  PSSP & 0.0009 & -0.0013 & 0.0246 & -0.1543 \\ 
   \hline
\end{tabular}
\end{table}

\begin{table}[ht]
\centering
\caption{Interaction coefficients for recruitment regressions in Idaho.} 
\begin{tabular}{rrrrr}
  \hline
 & ARTR & HECO & POSE & PSSP \\ 
  \hline
ARTR & -0.4054 & 0.2132 & 0.0120 & 0.2389 \\ 
  HECO & -0.5674 & -1.7722 & -0.1476 & -0.3184 \\ 
  POSE & -0.2499 & -0.0328 & -2.2873 & -0.1448 \\ 
  PSSP & -0.2580 & -0.1687 & 0.0365 & -1.7675 \\ 
   \hline
\end{tabular}
\end{table}

@@

\begin{table}[ht]
\centering
\caption{Interaction coefficients for survival regressions in Kansas.} 
\begin{tabular}{rrrr}
  \hline
 & BOCU & BOHI & SCSC \\ 
  \hline
BOCU & -0.1087 & 0.0006 & 0.0010 \\ 
  BOHI & 0.0021 & -0.0403 & -0.0153 \\ 
  SCSC & -0.0064 & -0.0066 & -0.0270 \\ 
   \hline
\end{tabular}
\end{table}

\begin{table}[ht]
\centering
\caption{Interaction coefficients for recruitment regressions in Kansas.} 
\begin{tabular}{rrrr}
  \hline
 & BOCU & BOHI & SCSC \\ 
  \hline
BOCU & -1.1584 & -0.0242 & -0.0524 \\ 
  BOHI & 0.3387 & -0.8620 & 0.0123 \\ 
  SCSC & 0.0615 & -0.0308 & -0.9543 \\ 
   \hline
\end{tabular}
\end{table}

@@

\begin{table}[ht]
\centering
\caption{Interaction coefficients for growth regressions in Montana.} 
\begin{tabular}{rrrrr}
  \hline
 & BOGR & HECO & PASM & POSE \\ 
  \hline
BOGR & -0.0121 & -0.0002 & -0.0229 & -0.0014 \\ 
  HECO & -0.0023 & -0.0778 & 0.0142 & 0.0061 \\ 
  PASM & -0.0005 & -0.0039 & -0.0601 & -0.0033 \\ 
  POSE & 0.0005 & -0.0101 & -0.0404 & -0.1431 \\ 
   \hline
\end{tabular}
\end{table}

\begin{table}[ht]
\centering
\caption{Interaction coefficients for survival regressions in Montana.} 
\begin{tabular}{rrrrr}
  \hline
 & BOGR & HECO & PASM & POSE \\ 
  \hline
BOGR & -0.1280 & 0.0211 & 0.1243 & 0.0173 \\ 
  HECO & -0.0043 & -0.5661 & 0.1386 & 0.0013 \\ 
  PASM & 0.0001 & -0.0044 & -1.3046 & 0.0012 \\ 
  POSE & 0.0010 & 0.0085 & 0.1198 & -1.2434 \\ 
   \hline
\end{tabular}
\end{table}

\begin{table}[ht]
\centering
\caption{Interaction coefficients for recruitment regressions in Montana.} 
\begin{tabular}{rrrrr}
  \hline
 & BOGR & HECO & PASM & POSE \\ 
  \hline
BOGR & -0.8916 & -0.2522 & -0.1334 & 0.0610 \\ 
  HECO & 0.0852 & -1.4191 & -0.0685 & -0.0422 \\ 
  PASM & 0.1252 & 0.3093 & -4.1823 & 0.3032 \\ 
  POSE & 0.1577 & 0.4906 & 0.0709 & -1.7065 \\ 
   \hline
\end{tabular}
\end{table}

@@

\begin{table}[ht]
\centering
\caption{Interaction coefficients for growth regressions in New Mexico.} 
\begin{tabular}{rrr}
  \hline
 & BOER & SPFL \\ 
  \hline
BOER & -0.0045 & -0.0013 \\ 
  SPFL & -0.0041 & -0.0176 \\ 
   \hline
\end{tabular}
\end{table}

\begin{table}[ht]
\centering
\caption{Interaction coefficients for survival regressions in New Mexico.} 
\begin{tabular}{rrr}
  \hline
 & BOER & SPFL \\ 
  \hline
BOER & -0.1575 & -0.0040 \\ 
  SPFL & -0.0120 & -0.2807 \\ 
   \hline
\end{tabular}
\end{table}

\begin{table}[ht]
\centering
\caption{Interaction coefficients for recruitment regressions in New Mexico.} 
\begin{tabular}{rrr}
  \hline
 & BOER & SPFL \\ 
  \hline
BOER & -0.7631 & -0.6198 \\ 
  SPFL & -0.0684 & -2.5220 \\ 
   \hline
\end{tabular}
\end{table}

>>>>

\begin{figure}[!ht]
  \centering
      \includegraphics[width=6in]{./components/formatted_figures/environmental_variances_cover.png}
  \caption{Variance of percent cover for each species (along x-axes) in each site through time from simulations with only environmental stochasticity operating (IPM with no species interactions).}
\end{figure}

\begin{figure}[!ht]
  \centering
      \includegraphics[width=6in]{./components/formatted_figures/environmental_variances_pgr.png}
  \caption{Variance of per capita growth rates for each species (along x-axes) in each site through time from simulations with only environmental stochasticity operating (IPM with no species interactions).}
\end{figure}

\begin{figure}[!ht]
  \centering
      \includegraphics[width=6in]{./components/formatted_figures/demographic_variances_cover.png}
  \caption{Variance of percent cover for each species (along x-axes) in each site through time from simulations with only demographic stochasticity operating (IBM simulated on 5 by 5 meter landscape).}
\end{figure}

\begin{figure}[!ht]
  \centering
      \includegraphics[width=6in]{./components/formatted_figures/demographic_variances_pgr.png}
  \caption{Variance of per capita growth rates for each species (along x-axes) in each site through time from simulations with only demographic stochasticity operating (IBM simulated on 5 by 5 meter landscape).}
\end{figure}

\begin{figure}[!ht]
  \centering
      \includegraphics[width=3in]{./components/formatted_figures/formatted_figureS4.png}
  \caption{Community-wide synchrony of species' growth rates from model simulation experiments for the Idaho community with \textit{Artemisia tripartita} removed. Synchrony of species' growth rates are from simulation experiments with demographic stochasticity, environmental stochasticity, and interspecific competition present (``All Drivers''), demographic stochasticity removed (``No D.S.''), environmental stochasticity removed (``No E.S.''), interspecific competition removed (``No Comp.''), interspecific competition and demographic stochasticity removed (``No Comp. + No D.S.''), and interspecific competition and environmental stochasticity removed (``No Comp. + No E.S.''). Error bars represent the 2.5\% and 97.5\% quantiles from model simulations.}
\end{figure}

@@

In all tables, species codes are as follows (also see Table 1 in the
main text):

\begin{itemize}
\itemsep1pt\parskip0pt\parsep0pt
\item
  \emph{Bouteloua eriopoda} = BOER
\item
  \emph{Sporobolus flexuosus} = SPFL
\item
  \emph{Bouteloua rothrockii} = BORO
\item
  \emph{Bouteloua curtipendula} = BOCU
\item
  \emph{Bouteloua hirsuta} = BOHI
\item
  \emph{Schizachyrium scoparium} = SCSC
\item
  \emph{Bouteloua gracilis} = BOGR
\item
  \emph{Hesperostipa comata} = HECO
\item
  \emph{Pascopyrum smithii} = PASM
\item
  \emph{Poa secunda} = POSE
\item
  \emph{Artemisia tripartita} = ARTR
\item
  \emph{Pseudoroegneria spicata} = PSSP
\end{itemize}

\begin{table}[ht]
\centering
\caption{Comparisons between our analytical predictions and simulation results for synchrony of species' per capita growth rates. Analytical predictions represent two limiting cases where only demographic stochasticity is operating ($\phi_{R,\mathcal{M}_D}$) and where only environmental stochasticity is operating ($\phi_{R,\mathcal{M}_E}$). Simulated synchrony values come from our empirically-based, multi-species population models when simulated under conditions that match the limiting case conditions (e.g., environmental stochasticity and competition removed for $\mathcal{M}_D$).} 
{\normalsize
\begin{tabular}{lrrrr}
  \hline
Site & Predicted $\phi_{R,\mathcal{M}_D}$ & Simulated $\phi_{R,\mathcal{M}_D}$ & Predicted $\phi_{R,\mathcal{M}_E}$ & Simulated $\phi_{R,\mathcal{M}_E}$ \\ 
  \hline
New Mexico & 0.56 & 0.51 & 0.86 & 0.86 \\ 
  Arizona & 0.51 & 0.52 & 0.82 & 0.81 \\ 
  Kansas & 0.35 & 0.39 & 0.62 & 0.62 \\ 
  Montana & 0.31 & 0.31 & 0.47 & 0.50 \\ 
  Idaho & 0.29 & 0.31 & 0.43 & 0.42 \\ 
   \hline
\end{tabular}
}
\end{table}

\begin{table}[ht]
\centering
\caption{Percent differences of synchrony of per capita growth rates between each removal simulation experiment and the 'All Drivers' simulation.} 
\begin{tabular}{lrrrrr}
  \hline
simulation & 1New Mexico & 2Arizona & 3Kansas & 4Montana & 5Idaho \\ 
  \hline
1No D.S. & 5.53 & 4.28 & 6.01 & 5.27 & 11.95 \\ 
  2No Comp. + No D.S. & 5.56 & 2.06 & 7.03 & 6.21 & 9.10 \\ 
  4No Comp. & 0.98 & 0.06 & 4.84 & 1.43 & 0.11 \\ 
  5No E.S. & 40.14 & 33.20 & 47.84 & 39.06 & 9.28 \\ 
  6No Comp. + No E.S. & 45.95 & 41.48 & 38.21 & 39.44 & 20.33 \\ 
   \hline
\end{tabular}
\end{table}

\begin{table}[ht]
\centering
\caption{Correlations of species' year random effects for each site by term, where term refers to the random effect on the slope or the intercept.} 
\begin{tabular}{llrrr}
  \hline
site & term & growth & recruit & surv \\ 
  \hline
Arizona & intercept & 0.51 & -0.05 & 0.51 \\ 
  Arizona & slope & 0.68 &  & 0.16 \\ 
  Idaho & intercept & 0.45 & 0.38 & 0.25 \\ 
  Idaho & slope & 0.50 &  & 0.47 \\ 
  Kansas & intercept & 0.44 & 0.29 & 0.26 \\ 
  Kansas & slope & 0.19 &  & 0.16 \\ 
  Montana & intercept & 0.29 & 0.07 & 0.41 \\ 
  Montana & slope & 0.11 &  & 0.02 \\ 
  NewMexico & intercept & 0.51 & -0.15 & 0.65 \\ 
  NewMexico & slope & 0.37 &  & 0.20 \\ 
   \hline
\end{tabular}
\end{table}

\begin{table}[ht]
\centering
\caption{Average interaction coefficients for each vital rate for each community.} 
\begin{tabular}{llrrr}
  \hline
Site & Interaction Type & Growth & Recruitment & Survival \\ 
  \hline
Arizona & Interspecific & -0.0111 & -0.4534 & -0.0507 \\ 
  Arizona & Intraspecific & -0.0402 & -1.4209 & -0.4446 \\ 
  Idaho & Interspecific & 0.0022 & -0.1091 & 0.0059 \\ 
  Idaho & Intraspecific & -0.0469 & -1.5569 & -0.5269 \\ 
  Kansas & Interspecific & -0.0008 & 0.0463 & -0.0041 \\ 
  Kansas & Intraspecific & -0.0062 & -0.9945 & -0.0586 \\ 
  Montana & Interspecific & -0.0059 & 0.0691 & 0.0342 \\ 
  Montana & Intraspecific & -0.0801 & -2.0900 & -0.8652 \\ 
  NewMexico & Interspecific & -0.0027 & -0.3461 & -0.0080 \\ 
  NewMexico & Intraspecific & -0.0111 & -1.6473 & -0.2191 \\ 
   \hline
\end{tabular}
\end{table}

@@

\begin{table}[ht]
\centering
\caption{Interaction coefficients for survival regressions in Arizona.} 
\begin{tabular}{rrr}
  \hline
 & BOER & BORO \\ 
  \hline
BOER & -0.2791 & -0.0814 \\ 
  BORO & -0.0200 & -0.6102 \\ 
   \hline
\end{tabular}
\end{table}

\begin{table}[ht]
\centering
\caption{Interaction coefficients for recruitment regressions in Arizona.} 
\begin{tabular}{rrr}
  \hline
 & BOER & BORO \\ 
  \hline
BOER & -0.5184 & -0.3290 \\ 
  BORO & -0.5779 & -2.3235 \\ 
   \hline
\end{tabular}
\end{table}

@@

\begin{table}[ht]
\centering
\caption{Interaction coefficients for survival regressions in Idaho.} 
\begin{tabular}{rrrrr}
  \hline
 & ARTR & HECO & POSE & PSSP \\ 
  \hline
ARTR & -0.0236 & -0.0199 & 0.0314 & 0.0158 \\ 
  HECO & -0.0005 & -1.0206 & -0.0051 & 0.0125 \\ 
  POSE & 0.0001 & 0.0006 & -0.9088 & 0.0121 \\ 
  PSSP & 0.0009 & -0.0013 & 0.0248 & -0.1547 \\ 
   \hline
\end{tabular}
\end{table}

\begin{table}[ht]
\centering
\caption{Interaction coefficients for recruitment regressions in Idaho.} 
\begin{tabular}{rrrrr}
  \hline
 & ARTR & HECO & POSE & PSSP \\ 
  \hline
ARTR & -0.4003 & 0.2243 & 0.0117 & 0.2360 \\ 
  HECO & -0.5681 & -1.7594 & -0.1437 & -0.3195 \\ 
  POSE & -0.2505 & -0.0131 & -2.2928 & -0.1420 \\ 
  PSSP & -0.2405 & -0.1389 & 0.0347 & -1.7751 \\ 
   \hline
\end{tabular}
\end{table}

@@

\begin{table}[ht]
\centering
\caption{Interaction coefficients for survival regressions in Kansas.} 
\begin{tabular}{rrrr}
  \hline
 & BOCU & BOHI & SCSC \\ 
  \hline
BOCU & -0.1084 & 0.0006 & 0.0010 \\ 
  BOHI & 0.0021 & -0.0403 & -0.0153 \\ 
  SCSC & -0.0064 & -0.0066 & -0.0271 \\ 
   \hline
\end{tabular}
\end{table}

\begin{table}[ht]
\centering
\caption{Interaction coefficients for recruitment regressions in Kansas.} 
\begin{tabular}{rrrr}
  \hline
 & BOCU & BOHI & SCSC \\ 
  \hline
BOCU & -1.1544 & -0.0312 & -0.0643 \\ 
  BOHI & 0.3410 & -0.8681 & 0.0041 \\ 
  SCSC & 0.0619 & -0.0336 & -0.9611 \\ 
   \hline
\end{tabular}
\end{table}

@@

\begin{table}[ht]
\centering
\caption{Interaction coefficients for growth regressions in Montana.} 
\begin{tabular}{rrrrr}
  \hline
 & BOGR & HECO & PASM & POSE \\ 
  \hline
BOGR & -0.0124 & -0.0032 & -0.0258 & -0.0001 \\ 
  HECO & -0.0025 & -0.0976 & 0.0096 & 0.0079 \\ 
  PASM & -0.0006 & -0.0041 & -0.0695 & -0.0030 \\ 
  POSE & 0.0006 & -0.0082 & -0.0417 & -0.1410 \\ 
   \hline
\end{tabular}
\end{table}

\begin{table}[ht]
\centering
\caption{Interaction coefficients for survival regressions in Montana.} 
\begin{tabular}{rrrrr}
  \hline
 & BOGR & HECO & PASM & POSE \\ 
  \hline
BOGR & -0.1316 & 0.0076 & 0.1096 & 0.0126 \\ 
  HECO & -0.0028 & -0.7064 & 0.1423 & -0.0030 \\ 
  PASM & -0.0012 & -0.0033 & -1.4026 & 0.0024 \\ 
  POSE & 0.0014 & 0.0082 & 0.1363 & -1.2203 \\ 
   \hline
\end{tabular}
\end{table}

\begin{table}[ht]
\centering
\caption{Interaction coefficients for recruitment regressions in Montana.} 
\begin{tabular}{rrrrr}
  \hline
 & BOGR & HECO & PASM & POSE \\ 
  \hline
BOGR & -0.9151 & -0.3076 & -0.0984 & 0.0495 \\ 
  HECO & -0.0785 & -1.4192 & -0.0480 & -0.0468 \\ 
  PASM & -0.0103 & 0.2773 & -4.3148 & 0.3470 \\ 
  POSE & 0.1971 & 0.4854 & 0.0623 & -1.7109 \\ 
   \hline
\end{tabular}
\end{table}

@@

\begin{table}[ht]
\centering
\caption{Interaction coefficients for growth regressions in NewMexico.} 
\begin{tabular}{rrr}
  \hline
 & BOER & SPFL \\ 
  \hline
BOER & -0.0045 & -0.0013 \\ 
  SPFL & -0.0041 & -0.0176 \\ 
   \hline
\end{tabular}
\end{table}

\begin{table}[ht]
\centering
\caption{Interaction coefficients for survival regressions in NewMexico.} 
\begin{tabular}{rrr}
  \hline
 & BOER & SPFL \\ 
  \hline
BOER & -0.1576 & -0.0040 \\ 
  SPFL & -0.0120 & -0.2806 \\ 
   \hline
\end{tabular}
\end{table}

\begin{table}[ht]
\centering
\caption{Interaction coefficients for recruitment regressions in NewMexico.} 
\begin{tabular}{rrr}
  \hline
 & BOER & SPFL \\ 
  \hline
BOER & -0.7649 & -0.6230 \\ 
  SPFL & -0.0691 & -2.5296 \\ 
   \hline
\end{tabular}
\end{table}
